---
title: "01 Read data"
author: "JungHwan Yang"
date: "July 13, 2015"
output: html_document
---

## This is for classifying Twitter users of US Presidential Debate 1 & 3 and post debate coverage for the Debate 1 & 3.

To read the data without formatting errors, I had to read the .csv file in SPSS and saved in .sav; then read it from R.

The files named usprez1.sav and usprez3.sav contains range of tweets that start from five minute before the debates and about two hours after the debates.

#### Warning: When importing .csv or .txt in SPSS, you have to specify variable length.

Suggested time range:
(1) Five minutes before each debate starts (approx. 90 minutes)
(2) Two hours after each debate (approx. 120 minutes)

Here I want to import those two files into R and make .RData file.

```{r Read raw data}
# Read usprez1.sav data
library(foreign)
path1 <- "../data//usprez1.sav" 
d1 <- read.spss(path1, use.value.labels = F, to.data.frame = T)
rm(path1)

# Read usprez3.sav data
path3 <- "../data//usprez3.sav" 
d3 <- read.spss(path3, use.value.labels = F, to.data.frame = T)
rm(path3)
```

I found some cell in d1 has some errors (probably because of , or some encoding errors). I merge two variables into one.

```{r}
# Merge cells with some errors
d1$V7 <- paste(d1$V7, d1$V70, sep = ""); d1$V70 <- NULL

# Change NULL values("\\N") into NA
# Since there's some weired character error in d1, I have to use sapply()
d1 <- as.data.frame(sapply(d1, gsub, pattern = "\\N", replacement = NA))
d1[d3 == "\\N"] <- NA
d3[d3 == "\\N"] <- NA
```


```{r}

```
## Save this file as usprez13.RData for further use