---
title: "02 Random sample for human coding and test ICR"
author: "JungHwan Yang"
date: "July 13, 2015"
output: html_document
---

#### Make a random sampled dataset

For human coding, pick a random sample from the raw data set

```{r}
# library(dplyr)
# set.seed(7)
# d13.rdm10k <- sample_n(d13, 10000)
```

For distribution of the file, export it as .xls file

```{r}
# library(xlsx)
# write.xlsx(d13.rdm10k, file="../data/usprez13-rdm10k.xlsx")
```

#### Test intercoder reliability

Three pairs of coders (total six coders) have coded either 300 or 500 tweets. Here's code to test intercoder reliability (ICR).

To make it easier, I make a .csv file that contains six coders codings in a following form:

| number | bs | mo | number | rk | yz | number | jy | md |
|--------|----|----|--------|----|----|--------|----|----|
|        |    |    |        |    |    |        |    |    |



```{r}
# coding100 <- read.csv("Data/korandom100coding.csv") # This file contains 48 tweets of the second round coding (63-110)
# library(irr)
# kripp.alpha(t(as.matrix(coding100[,])), method = "nominal")
# # Alpha = .746, which isacceptable. So, coders coded other tweets.
```