---
title: "02 Random sample for human coding and test ICR"
author: "JungHwan Yang"
date: "July 13, 2015"
output: html_document
---

#### Make a random sampled dataset

For human coding, pick a random sample from the raw data set

```{r}
# library(dplyr)
# set.seed(7)
# d13.rdm10k <- sample_n(d13, 10000)
```

For distribution of the file, export it as .xls file

```{r}
# library(xlsx)
# write.xlsx(d13.rdm10k, file="../data/usprez13-rdm10k.xlsx")
```

#### Test intercoder reliability

Three pairs of coders (total six coders) have coded either 300 or 500 tweets. Here's code to test intercoder reliability (ICR).

To make it easier, I make a .csv file that contains six coders codings in a following form:

| number | bs | mo | number | rk | yz | number | jy | md |
|--------|----|----|--------|----|----|--------|----|----|
|        |    |    |        |    |    |        |    |    |

Test intercoder reliability of the first 500 tweets

```{r}
library(irr)
us500coded <- read.csv("..//humancoding/first500codings/usprez500coded.csv")

coder1 <- us500coded[1:499, c(2:3)]
coder2 <- us500coded[1:337, c(5:6)]
coder3 <- us500coded[1:500, c(8:9)]

kripp.alpha(t(as.matrix(coder1[,])), method = "nominal")
kripp.alpha(t(as.matrix(coder2[,])), method = "nominal")
kripp.alpha(t(as.matrix(coder3[,])), method = "nominal")

```

Test intercoder reliability of the second 300 tweet

```{r}
us300coded <- read.csv("..//humancoding/second300codings/usprez300coded2nd.csv")

coder1 <- us300coded[1:300, c(2:3)]
coder2 <- us300coded[1:299, c(5:6)]
coder3 <- us300coded[1:300, c(8:9)]

kripp.alpha(t(as.matrix(coder1[,])), method = "nominal") # .59 Ben & Margarita
kripp.alpha(t(as.matrix(coder2[,])), method = "nominal") # .66 Rachel & Yini
kripp.alpha(t(as.matrix(coder3[,])), method = "nominal") # .75 Megan & J
```

Since coder1 (Ben and Margarita) and coder2 (Rachel and Yini) showed low intercoder reliabiliy, I tried to code some of their tweets and test ICR among three coders.

```{r}
us300coded3coders <- 
  read.csv("..//humancoding/second300codings/usprez300coded2nd-3coders.csv")

coder1.1 <- us300coded3coders[1:200, c(2:4)]
coder1.2 <- us300coded3coders[1:200, c(2, 4)]
coder1.3 <- us300coded3coders[1:200, c(3, 4)]
kripp.alpha(t(as.matrix(coder1.1[,])), method = "nominal") # .69 Ben, Margarita, & J
kripp.alpha(t(as.matrix(coder1.2[,])), method = "nominal") # .80 Ben & J
kripp.alpha(t(as.matrix(coder1.3[,])), method = "nominal") # .69 Margarita & J

coder2.1 <- us300coded3coders[1:200, c(6:8)]
coder2.2 <- us300coded3coders[1:200, c(6, 8)]
coder2.3 <- us300coded3coders[1:200, c(7, 8)]
kripp.alpha(t(as.matrix(coder2.1[,])), method = "nominal") # .71 Rachel, Yini, & J
kripp.alpha(t(as.matrix(coder2.2[,])), method = "nominal") # .73 Rachel & J
kripp.alpha(t(as.matrix(coder2.3[,])), method = "nominal") # .75 Yini & J
```
